---
title: "04.04.02-Quiz Notebook"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

Import the .R files to the environment;
```{r}
source("best.R")
source("rankhospital.R")
source("rankall.R")
```

### Question 1
What result is returned by the following code?
```
best("SC", "heart attack")
```
```{r Question 1, echo=TRUE}
best("SC", "heart attack")
```

### Question 2
What result is returned by the following code?
```
best("NY", "pneumonia")
```
```{r Question 2, echo=TRUE}
best("NY", "pneumonia")
```

### Question 3
What result is returned by the following code?
```
best("AK", "pneumonia")
```
```{r Question 3, echo=TRUE}
best("AK", "pneumonia")
```

### Question 4
What result is returned by the following code?
```
rankhospital("NC", "heart attack", 
  "worst")
```
```{r Question 4, echo=TRUE}
rankhospital("NC", "heart attack", 
  "worst")
```

### Question 5
What result is returned by the following code?
```
rankhospital("WA", "heart attack", 7)
```
```{r Question 5, echo=TRUE}
rankhospital("WA", "heart attack", 7)
```

### Question 6
What result is returned by the following code?
```
rankhospital("TX", "pneumonia", 10)
```
```{r Question 6, echo=TRUE}
rankhospital("TX", "pneumonia", 10)
```

### Question 7
What result is returned by the following code?
```
rankhospital("NY", "heart attack", 7)
```
```{r Question 7, echo=TRUE}
rankhospital("NY", "heart attack", 7)
```

### Question 8
What result is returned by the following code?
```
r <- rankall("heart attack", 4)
as.character(subset(r, state == "HI")$hospital)
```
```{r Question 8, echo=TRUE}
r <- rankall("heart attack", 4)
as.character(subset(r, state == "HI")$hospital)
```

### Question 9
What result is returned by the following code?
```
r <- rankall("pneumonia", "worst")
as.character(subset(r, state == "NJ")$hospital)
```
```{r Question 9, echo=TRUE}
r <- rankall("pneumonia", "worst")
as.character(subset(r, state == "NJ")$hospital)
```

### Question 10
What result is returned by the following code?
```
r <- rankall("heart failure", 10)
as.character(subset(r, state == "NV")$hospital)
```
```{r Question 10, echo=TRUE}
r <- rankall("heart failure", 10)
as.character(subset(r, state == "NV")$hospital)
```
