---
title: "Programming Assignment 3"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

# 1 Plot the 30-day mortality rates for heart attack 
Read the outcome data into R via the `read.csv` function and look at the first few rows.
```{r, echo=TRUE}
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
#head(outcome)
```

To make a simple histogram of the 30-day death rates from heart attack (column 11 in the outcome dataset), run
```{r, echo=TRUE}
outcome[, 11] <- as.numeric(outcome[, 11])
## You may get a warning about NAs being introduced; that is okay
hist(outcome[, 11])
```

# 2 Finding the best hospital in a state
Write a function called best that take two arguments: the 2-character abbreviated name of a state and an outcome name. The function reads the `outcome-of-care-measures.csv` file and returns a character vector with the name of the hospital that has the best (i.e. lowest) 30-day mortality for the specified outcome in that state. The hospital name is the name provided in the `Hospital.Name` variable. The outcomes can be one of “heart attack”, “heart failure”, or “pneumonia”. Hospitals that do not have data on a particular outcome should be excluded from the set of hospitals when deciding the rankings. Handling ties. If there is a tie for the best hospital for a given outcome, then the hospital names should be sorted in alphabetical order and the first hospital in that set should be chosen (i.e. if hospitals “b”, “c”, and “f” are tied for best, then hospital “b” should be returned).

```{r Finding the best hospital in a state, echo=TRUE}
source("best.R")
best("TX", "heart attack")
best("TX", "heart failure")
best("MD", "heart attack")
best("MD", "pneumonia")
#best("BB", "heart attack")
#best("NY", "hert attack")
```

# 3 Ranking hospitals by outcome in a state
Write a function called `rankhospital` that takes three arguments: the 2-character abbreviated name of a state (`state`), an outcome (`outcome`), and the ranking of a hospital in that state for that outcome (num). The function reads the `outcome-of-care-measures.csv` file and returns a character vector with the name of the hospital that has the ranking specified by the `num` argument. For example, the call
```
rankhospital("MD", "heart failure", 5)
```
would return a character vector containing the name of the hospital with the 5th lowest 30-day death rate for heart failure. The num argument can take values “best”, “worst”, or an integer indicating the ranking (smaller numbers are better). If the number given by num is larger than the number of hospitals in that state, then the function should return `NA`. Hospitals that do not have data on a particular outcome should be excluded from the set of hospitals when deciding the rankings. Handling ties. It may occur that multiple hospitals have the same 30-day mortality rate for a given cause of death. In those cases ties should be broken by using the hospital name.

```{r Ranking hospitals by outcome in a state, echo=TRUE}
source("rankhospital.R")
rankhospital("TX", "heart failure", 4)
rankhospital("MD", "heart attack", "worst")
rankhospital("MN", "heart attack", 5000)
```

# 4 Ranking hospitals in all states

Write a function called rankall that takes two arguments: an outcome name (`outcome`) and a hospital ranking (`num`). The function reads the outcome-of-care-measures.csv file and returns a 2-column data frame containing the hospital in each state that has the ranking specified in num. For example the function call `rankall("heart attack", "best")` would return a data frame containing the names of the hospitals that are the best in their respective states for 30-day heart attack death rates. The function should return a value for every state (some may be `NA`). The first column in the data frame is named `hospital`, which contains the hospital name, and the second column is named `state`, which contains the 2-character abbreviation for the state name. Hospitals that do not have data on a particular outcome should be excluded from the set of hospitals when deciding the rankings.
Handling ties. The `rankall` function should handle ties in the 30-day mortality rates in the same way that the `rankhospital` function handles ties.

```{r Ranking hospitals in all states, echo=TRUE}
source("rankall.R")
head(rankall("heart attack", 20), 10)
tail(rankall("pneumonia", "worst"), 3)
tail(rankall("heart failure"), 10)
```
